Trends of SDR in Thessaloniki 

### 2022-10-05 Article.Rmd
Commit 2022-10-05 13:07

---
title:         "Trends of SDR over Thessaloniki"
# author:        "Natsis Athanasios"
# institute:     "AUTH"
# affiliation:   "Laboratory of Atmospheric Physics"
abstract:      "Read "

@@

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      no
    keep_tex:         no
    keep_rmd:         yes
    latex_engine:     xelatex
    toc:              yes
    fig_width:        7
    fig_height:       4.5
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

####_  Document options _####

```
```{r echo=F, include=F}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
# knitr::opts_chunk$set(dev        = "png"    )
knitr::opts_chunk$set(out.width  = "85%"   )
knitr::opts_chunk$set(fig.align  = "center" )
knitr::opts_chunk$set(cache      =  T       )
# knitr::opts_chunk$set(fig.pos    = '!h'    )

```
```{r include=F, echo=F}
####  Set environment  ####
Sys.setenv(TZ = "UTC")
tic <- Sys.time()
Script.Name <- tryCatch({ funr::sys.script() },
                        error = function(e) { cat(paste("\nUnresolved script name: ", e),"\n\n")
                            return("Climatological_") })
if(!interactive()) {
    pdf(  file = paste0("~/Aerosols/REPORTS/runtime/", basename(sub("\\.R$",".pdf", Script.Name))))
    sink( file = paste0("~/Aerosols/REPORTS/runtime/", basename(sub("\\.R$",".out", Script.Name))), split=TRUE)
    filelock::lock(paste0("~/Aerosols/LOGs/",  basename(sub("\\.R$",".lock", Script.Name))), timeout = 0)
}

@@

## FIXME this is for pdf output
# options(warn=-1) ## hide warnings
# options(warn=2)  ## stop on warnings

```
```{r echo=F, include=T}
####  External code  ####
library(data.table, quietly = T, warn.conflicts = F)
library(pander,     quietly = T, warn.conflicts = F)

## Functions from `https://github.com/thanasisn/IStillBreakStuff/tree/main/FUNCTIONS/R`
source("~/CODE/FUNCTIONS/R/sumNA.R")
source("~/CODE/FUNCTIONS/R/linear_regrassion_capture.R")
source("~/CODE/FUNCTIONS/R/trig_deg.R")

@@

TEST      <- TRUE

MIN_ELEVA  <- 5  ## use data when sun above that
SZA_BIN    <- 1
MIN_N      <- 4
SEAS_MIN_N <- 3

@@

@@

        DATA <- rbind(temp, DATA, fill = TRUE)
        rm(temp)
    }
    ## this is used by old scripts
    myRtools::write_RDS(object = DATA, file = CS_file)
} else {
    cat(paste("Load data from Clear Sky proccess from parsed\n"))
    DATA <- readRDS(CS_file)
}
```

### Filter min elevation
Keep data with Sun elevation above `r MIN_ELEVA`

```{r }
DATA <- DATA[ Elevat >= MIN_ELEVA ]
```

### Bais paper obstacle filter

```{r }
DATA <- DATA[ ! (Azimuth > 35 & Azimuth < 120 & Elevat < 10) ]
```
```{r echo=F, include=T}
```

### Keep only data characterized as 'good' by the Radiation Quality control procedure

```{r echo=F, include=T}
DATA[ QCF_DIR != "good", wattDIR := NA ]
DATA[ QCF_DIR != "good", QCF_DIR := NA ]
DATA[ QCF_GLB != "good", wattGLB := NA ]
DATA[ QCF_GLB != "good", QCF_GLB := NA ]
DATA <- DATA[ ! (is.na(wattDIR) & is.na(wattGLB))  ]

## exclude some data for each instrument
# DATA[ QCF_DIR == "Extremely rare limits min (3)", wattDIR := NA ]
# DATA[ QCF_DIR == "Extremely rare limits min (3)", QCF_DIR := NA ]
#
# dirtb <- table(DATA$QCF_DIR)
# for (aty in names(dirtb)[!names(dirtb) %in% "good"]) {
#     temp <- DATA[ QCF_DIR == aty ]
#     cat(nrow(temp),aty,"\n")
# }
# glbtb <- table(DATA$QCF_GLB)
# for (aty in names(glbtb)[!names(glbtb) %in% "good"]) {
#     temp <- DATA[ QCF_GLB == aty ]
#     cat(nrow(temp),aty,"\n")
# }
```

## Data preparation
### Move measurements to mean earth distance

```{r }
DATA[ , wattDIR_1au := wattDIR * (sun_dist ^ 2) ]
DATA[ , wattGLB_1au := wattGLB * (sun_dist ^ 2) ]
```
```{r echo=F, include=T}
```

### Relative to actual TSI at 1au variable representation

```{r }
DATA[ , DIR_att := wattDIR_1au / tsi_1au_comb ]
DATA[ , GLB_att := wattGLB_1au / tsi_1au_comb ]
```

Using the actual values gives similar trends.

# #' ### Use original variable representation
# DATA[ , DIR_att := wattDIR_1au ]
# DATA[ , GLB_att := wattGLB_1au ]
# #+ echo=F, include=T

# #' ### Ground effect removal?
# #' Aerosol direct effects on global solar shortwave irradiance at high mountainous station Musala Bulgaria_Nojarov2021.pdf
# DATA$wattGLB_1au <- DATA$wattGLB_1au / cosde(DATA$SZA)
# DATA$wattDIR_1au <- DATA$wattDIR_1au / cosde(DATA$SZA)
# #+ echo=F, include=T
```

### Calculate Bouguer atmospheric transparency
see: Changes in solar radiation and their influence on temperature trend in Estonia 1955 2007_Russak2009.pdf

```{r }
DATA[, DIR_transp := ( wattDIR_1au / tsi_1au_comb ) ^ ( 1 / cosde(SZA) ) ]
```
```{r echo=F, include=T}

## fix noon just in case
DATA[ Azimuth <= 180 , preNoon := TRUE  ]
DATA[ Azimuth >  180 , preNoon := FALSE ]
```

### Split data to Clear Sky and non Clear sky
Method based and adapted to site from: Identification of Periods of Clear Sky
Irradiance in Time Series of GHI Measurements
_Matthew J. Reno and Clifford W. Hansen_.

```{r echo=F, include=T}
DATA_all   <- DATA

wecare     <- grep("CSflag_", names(DATA), value = T)
## use only cm21 flags
wecare     <- grep("_11", wecare, invert = T, value = T)
DATA_Clear <- DATA[ rowSums( DATA[, ..wecare ], na.rm = T ) == 0, ]
```
```{r echo=F, include=T}

## old flags
# DATA_Clear <- DATA_all[ CSflag == 0 ]
rm(DATA)

# #### . . My CSid method   ####
# #'
# #' | CS Flag | Test |
# #' |:-------:|:--------------------------------------------------------------|
# #' |   NA    | Undefined, untested                                           |
# #' |    0    | Passed as clear sky                                           |
# #' |    1    | Mean value of irradiance during the time period (MeanVIP)     |
# #' |    2    | Max Value of Irradiance during the time Period (MaxVIP)       |
# #' |    3    | Variability in irradiance by the length (VIL)                 |
# #' |    4    | Variance of Changes in the Time series (VCT)                  |
# #' |    5    | Variability in the Shape of the irradiance Measurements (VSM) |
# #' |    6    | Low Direct Irradiance limit (LDI)                             |
# #' |    7    | Low Global Irradiance limit (LGI)                             |
# #' |    8    | Too Few CS point for the day (FCS)                            |
# #' |    9    | Too Few data points for the day                               |
# #' |   10    | Missing Data                                                  |
# #' |   11    | Direct irradiance simple threshold                            |

#### 1. Long term anomaly trends ####
```

## 1. Long term anomaly trends

```{r }
##TODO t-test and significance
```

#### Calculate daily means ####

ALL_daily_mean <- DATA_all[, .(DIR_att       = mean(DIR_att,    na.rm = T),
                               GLB_att       = mean(GLB_att,    na.rm = T),
                               DIR_transp    = mean(DIR_transp, na.rm = T),
                               DIR_att_sd    = sd(  DIR_att,    na.rm = T),
                               GLB_att_sd    = sd(  GLB_att,    na.rm = T),
                               DIR_transp_sd = sd(DIR_transp, na.rm = T),
                               doy           = yday(Date),
                               GLB_att_N     = sum(!is.na(GLB_att)),
                               DIR_att_N     = sum(!is.na(DIR_att))  ),
                           by = .( Date = Day ) ]

CLEAR_daily_mean <- DATA_Clear[, .(DIR_att       = mean(DIR_att,    na.rm = T),
                                   GLB_att       = mean(GLB_att,    na.rm = T),
                                   DIR_transp    = mean(DIR_transp, na.rm = T),
                                   DIR_att_sd    = sd(  DIR_att,    na.rm = T),
                                   GLB_att_sd    = sd(  GLB_att,    na.rm = T),
                                   DIR_transp_sd = sd(DIR_transp, na.rm = T),
                                   doy           = yday(Date),
                                   GLB_att_N     = sum(!is.na(GLB_att)),
                                   DIR_att_N     = sum(!is.na(DIR_att))  ),
                               by = .( Date = Day ) ]
```

#### Margin of error calculation for 0.95 confidence interval ####

```{r echo=T, include=T}
CONF_INTERV <- .95
conf_param  <- 1-(1-CONF_INTERV)/2
suppressWarnings({
ALL_daily_mean[,  DIR_att_EM   := qt(conf_param,df=DIR_att_N -1) * DIR_att_sd    / sqrt(DIR_att_N)]
ALL_daily_mean[,  GLB_att_EM   := qt(conf_param,df=GLB_att_N -1) * GLB_att_sd    / sqrt(GLB_att_N)]
ALL_daily_mean[,  DIR_transp_EM:= qt(conf_param,df=DIR_att_N -1) * DIR_transp_sd / sqrt(DIR_att_N)]
CLEAR_daily_mean[,DIR_att_EM   := qt(conf_param,df=DIR_att_N -1) * DIR_att_sd    / sqrt(DIR_att_N)]
CLEAR_daily_mean[,GLB_att_EM   := qt(conf_param,df=GLB_att_N -1) * GLB_att_sd    / sqrt(GLB_att_N)]
CLEAR_daily_mean[,DIR_transp_EM:= qt(conf_param,df=DIR_att_N -1) * DIR_transp_sd / sqrt(DIR_att_N)]
})
```
```{r echo=F, include=F}
```

#### Exclude means with less than `r SUM_THRES` data points

```{r echo=F, include=T}
ALL_daily_mean[  DIR_att_N <= SUM_THRES, DIR_att    := NA ]
ALL_daily_mean[  GLB_att_N <= SUM_THRES, GLB_att    := NA ]
ALL_daily_mean[  DIR_att_N <= SUM_THRES, DIR_transp := NA ]
CLEAR_daily_mean[DIR_att_N <= SUM_THRES, DIR_att    := NA ]
CLEAR_daily_mean[GLB_att_N <= SUM_THRES, GLB_att    := NA ]
CLEAR_daily_mean[DIR_att_N <= SUM_THRES, DIR_transp := NA ]
```

#### Calculate daily seasonal values ####

ALL_daily_seas <-
    ALL_daily_mean[, .(DIR_att_seas    = mean(DIR_att,    na.rm = T),
                       GLB_att_seas    = mean(GLB_att,    na.rm = T),
                       DIR_transp_seas = mean(DIR_transp, na.rm = T),
                       DIR_att_sd_seas = sd(  DIR_att,    na.rm = T),
                       GLB_att_sd_seas = sd(  GLB_att,    na.rm = T),
                       GLB_att_N_seas  = sum(!is.na(GLB_att)),
                       DIR_att_N_seas  = sum(!is.na(DIR_att))  ),
                   by = .( doy ) ]

CLEAR_daily_seas <-
    CLEAR_daily_mean[, .(DIR_att_seas    = mean(DIR_att,    na.rm = T),
                         GLB_att_seas    = mean(GLB_att,    na.rm = T),
                         DIR_transp_seas = mean(DIR_transp, na.rm = T),
                         DIR_att_sd_seas = sd(  DIR_att,    na.rm = T),
                         GLB_att_sd_seas = sd(  GLB_att,    na.rm = T),
                         GLB_att_N_seas  = sum(!is.na(GLB_att)),
                         DIR_att_N_seas  = sum(!is.na(DIR_att))  ),
                     by = .( doy ) ]

```
```{r echo=F, include=F}
## ~ Plots longterm  ####
plot( ALL_daily_mean$Date, ALL_daily_mean$DIR_att )
plot( ALL_daily_mean$Date, ALL_daily_mean$GLB_att )
plot( ALL_daily_mean$Date, ALL_daily_mean$DIR_transp )

plot( ALL_daily_mean$doy, ALL_daily_mean$DIR_att )
plot( ALL_daily_mean$doy, ALL_daily_mean$GLB_att )
plot( ALL_daily_mean$doy, ALL_daily_mean$DIR_transp )

plot( ALL_daily_mean$doy, ALL_daily_mean$GLB_att_N)
plot( ALL_daily_mean$doy, ALL_daily_mean$DIR_att_N)

hist(ALL_daily_mean$DIR_att_N)
hist(ALL_daily_mean$GLB_att_N)

plot( CLEAR_daily_mean$Date, CLEAR_daily_mean$DIR_att )
plot( CLEAR_daily_mean$Date, CLEAR_daily_mean$GLB_att )
plot( CLEAR_daily_mean$Date, CLEAR_daily_mean$DIR_transp )

plot( CLEAR_daily_mean$doy,  CLEAR_daily_mean$DIR_att )
plot( CLEAR_daily_mean$doy,  CLEAR_daily_mean$GLB_att )
plot( CLEAR_daily_mean$doy,  CLEAR_daily_mean$DIR_transp )

plot( CLEAR_daily_mean$doy,  CLEAR_daily_mean$GLB_att_N)
plot( CLEAR_daily_mean$doy,  CLEAR_daily_mean$DIR_att_N)

hist( CLEAR_daily_mean$DIR_att_N)
hist( CLEAR_daily_mean$GLB_att_N)

## ~ Plots seasonal ####

plot( ALL_daily_seas$doy, ALL_daily_seas$DIR_att_seas )
plot( ALL_daily_seas$doy, ALL_daily_seas$GLB_att_seas )
plot( ALL_daily_seas$doy, ALL_daily_seas$DIR_transp_seas )
plot( ALL_daily_seas$doy, ALL_daily_seas$GLB_att_N_seas)
plot( ALL_daily_seas$doy, ALL_daily_seas$DIR_att_N_seas)

plot( CLEAR_daily_seas$doy, CLEAR_daily_seas$DIR_att_seas )
plot( CLEAR_daily_seas$doy, CLEAR_daily_seas$GLB_att_seas )
plot( CLEAR_daily_seas$doy, CLEAR_daily_seas$DIR_transp_seas )
plot( CLEAR_daily_seas$doy, CLEAR_daily_seas$GLB_att_N_seas)
plot( CLEAR_daily_seas$doy, CLEAR_daily_seas$DIR_att_N_seas)
```

#### Calculate seasonal anomaly ####

```{r echo=F, include=F}

ALL_daily_seas   <- merge(  ALL_daily_mean, ALL_daily_seas,   by = "doy", all = T)
CLEAR_daily_seas <- merge(CLEAR_daily_mean, CLEAR_daily_seas, by = "doy", all = T)

setorder(ALL_daily_seas,Date)
setorder(CLEAR_daily_seas,Date)

## anomaly
# ALL_daily_seas[   , DIR_att    := DIR_att    - DIR_att_seas    ]
# ALL_daily_seas[   , GLB_att    := GLB_att    - GLB_att_seas    ]
# ALL_daily_seas[   , DIR_transp := DIR_transp - DIR_transp_seas ]
# CLEAR_daily_seas[ , DIR_att    := DIR_att    - DIR_att_seas    ]
# CLEAR_daily_seas[ , GLB_att    := GLB_att    - GLB_att_seas    ]
# CLEAR_daily_seas[ , DIR_transp := DIR_transp - DIR_transp_seas ]

## relative anomaly
```
```{r echo=T, include=T}
ALL_daily_seas[  , DIR_att   := 100*( DIR_att    - DIR_att_seas    ) / DIR_att_seas    ]
ALL_daily_seas[  , GLB_att   := 100*( GLB_att    - GLB_att_seas    ) / GLB_att_seas    ]
ALL_daily_seas[  , DIR_transp:= 100*( DIR_transp - DIR_transp_seas ) / DIR_transp_seas ]
CLEAR_daily_seas[, DIR_att   := 100*( DIR_att    - DIR_att_seas    ) / DIR_att_seas    ]
CLEAR_daily_seas[, GLB_att   := 100*( GLB_att    - GLB_att_seas    ) / GLB_att_seas    ]
CLEAR_daily_seas[, DIR_transp:= 100*( DIR_transp - DIR_transp_seas ) / DIR_transp_seas ]
```
```{r echo=F, include=F}

#### ~ Plot of trends  ####
```

\newpage
## Trends on all sky conditions data

gather <- data.frame()
timefactor <- 1

plot(ALL_daily_seas$Date, ALL_daily_seas$DIR_att, pch  = ".", xlab = "" )
lm1 <- lm( DIR_att ~ Date , data = ALL_daily_seas)
gather <- rbind(gather,
                data.table(
                    var  = "DIR_att",
                    data = "ALL",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("All day daily Direct"),cex=0.9)

plot(ALL_daily_seas$Date, ALL_daily_seas$GLB_att, pch  = ".", xlab = "" )
lm1 <- lm( GLB_att ~ Date , data = ALL_daily_seas)
gather <- rbind(gather,
                data.table(
                    var  = "GLB_att",
                    data = "ALL",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("All sky daily Global"),cex=0.9)

plot(ALL_daily_seas$Date, ALL_daily_seas$DIR_transp, pch  = ".", xlab = "" )
lm1 <- lm( DIR_transp ~ Date , data = ALL_daily_seas)
gather <- rbind(gather,
                data.table(
                    var  = "DIR_transp",
                    data = "ALL",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("All sky daily Direct transparency"),cex=0.9)
```

\newpage
## Trends on clear sky data

plot(CLEAR_daily_seas$Date, CLEAR_daily_seas$DIR_att, pch  = ".", xlab = "" )
lm1 <- lm( DIR_att ~ Date , data = CLEAR_daily_seas)
gather <- rbind(gather,
                data.table(
                    var  = "DIR_att",
                    data = "CLEAR",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("Clear Sky daily Direct"),cex=0.9)

plot(CLEAR_daily_seas$Date, CLEAR_daily_seas$GLB_att, pch  = ".", xlab = "" )
lm1 <- lm( GLB_att ~ Date , data = CLEAR_daily_seas)
gather <- rbind(gather,
                data.table(
                    var  = "GBL_att",
                    data = "CLEAR",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("Clear Sky daily Global"),cex=0.9)

plot(CLEAR_daily_seas$Date, CLEAR_daily_seas$DIR_transp, pch  = ".", xlab = "" )
lm1 <- lm( DIR_transp ~ Date , data = CLEAR_daily_mean)
gather <- rbind(gather,
                data.table(
                    var  = "DIR_transp",
                    data = "CLEAR",
                    linear_regression_capture(lm1)
                )
)
abline(lm1)
fit <- lm1[[1]]
legend('top', lty = 1, bty = "n",
       paste('Y =', signif(fit[1],2),if(fit[2]>0)'+'else'-',signif(abs(fit[2]/timefactor*365),3),'* year'))
title(paste("Clear Sky daily Direct transparency"),cex=0.9)

wecare <- grep("intercept", names(gather), value = T, invert = T)
gather <- data.table(gather)
```

## Table of trends

```{r echo=F, include=T}
pprint <- gather[ , ..wecare]

pprint[, slope    := slope/timefactor*365 ]
pprint[, slope.sd := slope.sd/timefactor*365 ]

pander(pprint,
       cap = "Slope is in %/year")
```
```{r echo=F, include=F}

## Test plots of all variables
```
```{r echo=F, include=F}
data_list  <- list(ALL_daily_seas, CLEAR_daily_seas)
data_names <- list("All data points", "All clear sky data points")
by_var     <- "Date"
wecare     <- unique(unlist(lapply(data_list, names)))
wecare     <- grep(by_var, wecare, invert = T, value = T)
for(i in 1:length(data_list)) {
    Dplot <- data_list[[i]]
    cat(paste("\n\n## ", i, "\n\n"))
    for (var in wecare) {
        vect <- Dplot[[var]]
        hist(vect, main = var, breaks = 100)
        plot(Dplot[[by_var]], vect, pch = ".", main = var)
        # plot(Dplot$SZA, vect, pch = ".", main = var)
        # plot(Dplot$SZA, vect, pch = ".", main = var)
        # plot(cosde(Dplot$SZA), vect, pch = ".", main = var)
    }
}
```

@@

```{r include=T, echo=F}
tac <- Sys.time()
cat(sprintf("%s %s@%s %s %f mins\n\n",Sys.time(),Sys.info()["login"],Sys.info()["nodename"],Script.Name,difftime(tac,tic,units="mins")))
```

>>>>

---
title:         "Trends of SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics,AUTH, natsisthanasis@gmail.com]
  - Jane Doe^[Institution Two, jane@example.org]
abstract:
  "Study of GHI and DNI radiation for 'clear sky' and all sly conditions."

@@

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      no
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    fig_width:        7
    fig_height:       4.5
    cache:            yes
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

```{r echo=F, include=F}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
# knitr::opts_chunk$set(dev        = "png"    )
knitr::opts_chunk$set(out.width  = "80%"   )
knitr::opts_chunk$set(fig.align  = "center" )
# knitr::opts_chunk$set(fig.pos    = '!h'    )

####  Set environment  ####
Sys.setenv(TZ = "UTC")
tic <- Sys.time()

@@

library(data.table, quietly = T, warn.conflicts = F)
library(pander,     quietly = T, warn.conflicts = F)
## Functions from `https://github.com/thanasisn/IStillBreakStuff/tree/main/FUNCTIONS/R`
source("~/CODE/FUNCTIONS/R/sumNA.R")
source("~/CODE/FUNCTIONS/R/linear_regrassion_capture.R")
source("~/CODE/FUNCTIONS/R/trig_deg.R")

@@

MIN_ELEVA  <- 5  ## use data when sun above that
SZA_BIN    <- 1  ## bin size of SZA
MIN_N      <- 4
SEAS_MIN_N <- 3

@@

## Data description

....... span

...... measuremetns CHP1 CM21

....... screening

....... Quality assurance [cite]

## Data preperation

@@

        DATA <- rbind(temp, DATA, fill = TRUE)
        rm(temp)
    }
    ## this is used by old scripts
    myRtools::write_RDS(object = DATA, file = CS_file)
} else {
    # cat(paste("Load data from Clear Sky proccess from parsed\n"))
    DATA <- readRDS(CS_file)
}

```

Due to the large measurement assertenty near the horizon we exclude all measurements
with greater than SZA $`r 90-MIN_ELEVA`^\circ$. Moreover, due to nearby hills and buildings
we remove data with azimuth angle between $35^\circ$ and $120^\circ$ and SZA greater than $`r 90-10`^\circ$.

```{r echo=F}
DATA <- DATA[ Elevat >= MIN_ELEVA ]
DATA <- DATA[ ! (Azimuth > 35 & Azimuth < 120 & Elevat < 10) ]
```

@@

```{r include=T, echo=F}
tac <- Sys.time()
cat(sprintf("%s %s@%s %f mins\n\n",Sys.time(),Sys.info()["login"],Sys.info()["nodename"],difftime(tac,tic,units="mins")))
```
